Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/motivation.tex
typo

The second class, which occurred four times in our study is logic errors, where application code
misinterprets input data. Safe languages and exploit mitigation technologies do not help against
such vulnerabilities. This can lead to serious security consequences when two systems disagree on
the meaning of a network packet or a signed message, as shown by the vulnerabilities we described
before. CVE-2013-0211 shows that logic errors can be the underlying cause of memory corruption, when
one part of a parser interprets a size field as a signed integer and another interprets it as an
unsigned integer. CVE-2013-7338 is a logic error that allows an attacker to craft ZIP files that are
incorrectly extracted or result in applications hangs with applications using a Python ZIP library,
because this library does not check that two fields that contain the size of a file contain the same value.

These mistakes are highly application-specific, and
are difficult to mitigate using existing techniques, and these mistakes
can occur even in high-level languages that guarantee memory safety. By
allowing developers to specify their data format just once, Nail avoids
logic errors and inconsistencies in parsing and output generation.
e through endless loops
or incorrectly extracted ZIP files.

>>>>

The second class, which occurred four times in our study is logic errors, where application code
misinterprets input data. Safe languages and exploit mitigation technologies do not help against
such vulnerabilities. This can lead to serious security consequences when two systems disagree on
the meaning of a network packet or a signed message, as shown by the vulnerabilities we described
before. CVE-2013-0211 shows that logic errors can be the underlying cause of memory corruption, when
one part of a parser interprets a size field as a signed integer and another interprets it as an
unsigned integer. CVE-2013-7338 is a logic error that allows an attacker to craft ZIP files that are
incorrectly extracted or result in application hangs with applications using a Python ZIP library,
because this library does not check that two fields that contain the size of a file contain the same value.

These mistakes are highly application-specific, and
are difficult to mitigate using existing techniques, and these mistakes
can occur even in high-level languages that guarantee memory safety. By
allowing developers to specify their data format just once, Nail avoids
logic errors and inconsistencies in parsing and output generation.
